Plots and Data Summaries

### 2025-03-05 manuscript.qmd
Update folder structure of manuscript

---
title: 'From Archives to AI: Residential Property Data Across Three Decades in Brunei Darussalam'
authors:
  - name: Haziq Jamil
    orcid: 0000-0003-3298-1010
    email: haziq.jamil@ubd.edu.bn
    url: 'https://haziqj.ml'
    corresponding: true
    affiliations:
      - name: Universiti Brunei Darussalam
        id: ubd
        department: Mathematical Sciences, Faculty of Science
        address: Universiti Brunei Darussalam, Jalan Tungku Link
        city: Bandar Seri Begawan
        country: Brunei
        postal-code: BE 1410
  - name: Amira Barizah Noorosmawie
    affiliations:
      - ref: ubd        
  - name: Hafeezul Waezz Rabu
    affiliations:
      - ref: ubd
  - name: Lutfi Abdul Razak
    orcid: 0000-0003-1681-0895
    email: lutfi.razak@ubd.edu.bn
    affiliations:
      - name: UBD School of Business and Economics
        id: ubdsbe
        # department: Mathematical Sciences, Faculty of Science
        address: Universiti Brunei Darussalam, Jalan Tungku Link
        city: Bandar Seri Begawan
        country: Brunei
        postal-code: BE 1410         
date-modified: last-modified
abstract: |
  This article introduces the first publicly available data set for analyzing the Brunei housing market, covering 32,104 property listings from 1993 to early 2025. The data set, curated from property advertisements in newspapers and online platforms, includes key attributes such as price, location, property type, and physical characteristics, enriched with area-level spatial information. Comprehensive and historical, it complements the Brunei Darussalam Central Bank’s Residential Property Price Index (RPPI), addressing the limitations of restricted access to raw RPPI data and its relatively short timeline since its inception in 2015. Data collection involved manual transcription from archival sources and automated web scraping using programmatic methods, supported by innovative cleaning with Large Language Models (LLMs) to structure unformatted text. The data set enables spatial and temporal analysis, with potential applications in economics, urban planning, and real estate research. While minor limitations exist, such as missing values and spatial coverage bias toward the Brunei-Muara district, this data set provides a robust foundation for exploring housing market trends and informing policy decisions.
keywords:
  - Housing Market
  - Brunei
  - Property Listings
  - Spatial Data
  - Web Scraping
  - Large Language Models
---

```{r}
#| include: false
#| eval: true 
#| file: data.R
```

@@

:::: {.content-visible when-format="html"}
::: column-page
{{< embed analysis.qmd#tbl-summary >}}
:::
::::

:::: {.content-visible unless-format="html"}
::: landscape
{{< embed analysis.qmd#tbl-summary >}}
:::
::::

@@

{{< embed analysis.qmd#fig-spatial >}}

@@

{{< embed analysis.qmd#fig-price-evolution >}}

@@

{{< embed analysis.qmd#tbl-avail >}}

@@

{{< embed analysis.qmd#fig-corr >}}

@@

{{< embed analysis.qmd#fig-rppi >}}

@@

{{< embed analysis.qmd#fig-llmtest >}}

>>>>

---
title: 'From Archives to AI: Residential Property Data Across Three Decades in Brunei Darussalam'
authors:
  - name: Haziq Jamil
    orcid: 0000-0003-3298-1010
    email: haziq.jamil@ubd.edu.bn
    url: 'https://haziqj.ml'
    corresponding: true
    affiliations:
      - name: Universiti Brunei Darussalam
        id: ubd
        department: Mathematical Sciences, Faculty of Science
        address: Universiti Brunei Darussalam, Jalan Tungku Link
        city: Bandar Seri Begawan
        country: Brunei
        postal-code: BE 1410
  - name: Amira Barizah Noorosmawie
    affiliations:
      - ref: ubd        
  - name: Hafeezul Waezz Rabu
    affiliations:
      - ref: ubd
  - name: Lutfi Abdul Razak
    orcid: 0000-0003-1681-0895
    email: lutfi.razak@ubd.edu.bn
    affiliations:
      - name: UBD School of Business and Economics
        id: ubdsbe
        # department: Mathematical Sciences, Faculty of Science
        address: Universiti Brunei Darussalam, Jalan Tungku Link
        city: Bandar Seri Begawan
        country: Brunei
        postal-code: BE 1410         
date-modified: last-modified
abstract: |
  This article introduces the first publicly available data set for analyzing the Brunei housing market, covering 31,150 property listings from 1993 to early 2025. The data set, curated from property advertisements in newspapers and online platforms, includes key attributes such as price, location, property type, and physical characteristics, enriched with area-level spatial information. Comprehensive and historical, it complements the Brunei Darussalam Central Bank’s Residential Property Price Index (RPPI), addressing the limitations of restricted access to raw RPPI data and its relatively short timeline since its inception in 2015. Data collection involved manual transcription from archival sources and automated web scraping using programmatic methods, supported by innovative cleaning with Large Language Models (LLMs) to structure unformatted text. The data set enables spatial and temporal analysis, with potential applications in economics, urban planning, and real estate research. While minor limitations exist, such as missing values and spatial coverage bias toward the Brunei-Muara district, this data set provides a robust foundation for exploring housing market trends and informing policy decisions.
keywords:
  - Housing Market
  - Brunei
  - Property Listings
  - Spatial Data
  - Web Scraping
  - Large Language Models
---

```{r}
#| include: false
#| eval: true 
#| file: notebooks/data.R
```

@@

:::: {.content-visible when-format="html"}
::: column-page
{{< embed notebooks/analysis.qmd#tbl-summary >}}
:::
::::

:::: {.content-visible unless-format="html"}
::: landscape
{{< embed notebooks/analysis.qmd#tbl-summary >}}
:::
::::

@@

{{< embed notebooks/analysis.qmd#fig-spatial >}}

@@

{{< embed notebooks/analysis.qmd#fig-price-evolution >}}

@@

{{< embed notebooks/analysis.qmd#tbl-avail >}}

@@

{{< embed notebooks/analysis.qmd#fig-corr >}}

@@

{{< embed notebooks/analysis.qmd#fig-rppi >}}

@@

{{< embed notebooks/analysis.qmd#fig-llmtest >}}

### 2025-03-05 notebooks/analysis.qmd
Update folder structure of manuscript

hsp_rppi |>  
  pivot_longer(c(index, rppi), names_to = "series", values_to = "value") |>
  ggplot(aes(x = quarter, y = value, col = series)) +
  geom_hline(yintercept = 1, linetype = "dashed") +
  geom_line(linewidth = 0.8) +
  scale_colour_brewer(palette = "Set1") +
  scale_y_continuous(labels = scales::percent, name = "Index") +
  zoo::scale_x_yearqtr(
    format = "%Y-Q%q", 
    expand = c(0, 0.1),
    name = NULL, 
    breaks = seq(2015, 2024.5, by = 0.25)
  ) +
  theme_bw() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "none"
  ) +
  geom_text(
    data = tibble(
      quarter = c(2024.3 + 0.25, 2024.3 + 0.25),
      series = c("index", "rppi"),
      value = c(0.941, 0.955) - 0.02,
      label = c("Median PPSF", "RPPI (BDCB)")
    ),
    aes(label = label),
    hjust = 0
  ) +
  coord_cartesian(xlim = c(2015, 2025.75))
```

@@

```{r}
#| label: fig-llmtest
#| fig-cap: Model accuracy comparison using the LLM test data set.
#| fig-height: 4.5
#| fig-width: 9
#| out-width: 100%
load("experiments/llm_test.RData")
p_llm_test
```

>>>>

hsp_rppi |>  
  pivot_longer(c(index, rppi), names_to = "series", values_to = "value") |>
  ggplot(aes(x = quarter, y = value, col = series)) +
  geom_hline(yintercept = 1, linetype = "dashed") +
  geom_line(linewidth = 0.8) +
  scale_colour_brewer(palette = "Set1") +
  scale_y_continuous(labels = scales::percent, name = "Index") +
  zoo::scale_x_yearqtr(
    format = "%Y-Q%q", 
    expand = c(0, 0.1),
    name = NULL, 
    breaks = seq(2015, 2024.75, by = 0.25)
  ) +
  theme_bw() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "none"
  ) +
  geom_text(
    data = tibble(
      quarter = c(2024.3 + 0.25, 2024.3 + 0.25),
      series = c("index", "rppi"),
      value = c(0.941, 0.955) - 0.02,
      label = c("Median PPSF", "RPPI (BDCB)")
    ),
    aes(label = label),
    hjust = 0
  ) +
  coord_cartesian(xlim = c(2015, 2025.75))
```

@@

```{r}
#| label: fig-llmtest
#| fig-cap: Comparison of data extraction accuracy across multiple LLM models on the test dataset. Each bar represents the percentage of correctly extracted fields for a given model.
#| fig-height: 4.5
#| fig-width: 9
#| out-width: 100%
load(here::here("experiments/llm_test.RData"))
p_llm_test
```
